---
title: "Machine Learning for churn prediction"
author: Kamil Matuszelański
output: 
  bookdown::word_document2:
    reference_docx: resources/styles_template.docx
    number_sections: true
    # toc: true
    # toc_depth: 3
# output: html_document
bibliography: resources/bib.bibtex
always_allow_html: true
params:
  echo: False
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Abstract {-}

## Title {-}

Modeling customer churn in the context of e-commerce retail business

## Summary {-}

This study is an attempt to propose a model for customer churn prediction in the case of an e-commerce retail store operating in Brazil. Among the sets of features included in the models were transaction, location, geodemographic and perception variables. The results show that transaction features from the previous purchase are the main factor driving the customers' loyalty. 

## Keywords {-}

churn analysis, customer relationship management, topic modeling, geodemographics


## Title in polish {-}

Modelowanie odpływu klientów w biznesie e-commerce

&nbsp;

\pagebreak

<!-- :::{custom-style="chapters"} -->
<!-- chapter I -->
<!-- ::: -->

# Introduction {-}
```{r child = '01_introduction.Rmd'}
```

&nbsp;

\pagebreak

:::{custom-style="chapters"}
chapter I
:::

# Literature review
```{r child = '02_literature_review.Rmd'}
```

&nbsp;

\pagebreak

:::{custom-style="chapters"}
chapter II
:::

# Dataset description

```{r child = '03_dataset_description.Rmd'}
```

&nbsp;

\pagebreak

:::{custom-style="chapters"}
chapter III
:::

# Methods description

```{r child = '04_methods_description.Rmd'}
```

&nbsp;

\pagebreak

:::{custom-style="chapters"}
chapter IV
:::

# Results

```{r child = '05_results.Rmd'}
```

&nbsp;

\pagebreak

<!-- :::{custom-style="chapters"} -->
<!-- chapter VI -->
<!-- ::: -->

# Summary {-}

```{r child = '06_summary.Rmd'}
```

&nbsp;

\pagebreak

# Appendixes {-#appendixes}

```{r child = '07_appendix.Rmd'}
```

&nbsp;

\pagebreak



# References

